Open Science, Open Plant Pathology

### 2019-01-23 analysis/paper/paper.Rmd
Edits to paper text

---
title: "Open Science, Open Plant Pathology"
author:
  - Adam H. Sparks
  - Emerson Del Ponte
  - Sydney Everhart
  - Zachary Foster
  - Niklaus J Grünwald
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow. We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles failed to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproduciblity.
---

@@

Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved. Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management. Scientific research in the field vary from purely observational/descriptive nature to inferential based on experimental or simulation-derived data sets. Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available, beyond what is reported in the scientific article. These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawing and photographs, statistical analysis codes, among other data.

## Reproducible research

@@

## Open science

@@

# A general workflow

@@

A first level of reproducibility involves making available research materials such as strains and/or nucleic acid sequences in public collection and citations for methods used. A second level involves providing raw data and codes as binary files (PDF or other non-text file) in supplemental materials which do not allow prompt access to the data and running the codes because of use of expensive commercial software or a pay-wall. The highest level includes efforts to annotate structured raw data and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code. The first level as reported is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations. In the next section we present standards and tools that can be used to ensure reproducibility (Figure 1).

```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

@@

When making your science more open and reproducible, methods, software used (including things like R packages), etc. should be cited. This allows end users to identify what was used and identify the methods used more accurately. Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research. This also helps ensure that you as a researcher are able to reconstruct what you have done since you will have good notes and documentation.

@@

- provide full description for equipments, etc.
- rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/

@@

### Source code

>>>>

---
title: "Open Science, Open Plant Pathology"
author:
  - Adam H. Sparks
  - Emerson Del Ponte
  - Sydney Everhart
  - Zachary Foster
  - Niklaus J Grünwald
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow. We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles were not very open, failing to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
---

@@

Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved. Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve management. Scientific research in the field varies from the purely observational or descriptive nature to inferential based on experimental or simulation-derived data sets. Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article. These include biological materials (strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other data.

## Reproducible Research

@@

## Open Science

@@

# A General Workflow

@@

A first level of reproducibility involves openly available research materials such as strains and/or nucleic acid sequences in public collections and citations for methods used. A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall. The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code. The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations. In the next section we present standards and tools that can be used to ensure reproducibility \@ref(fig:workflow-dia).

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, results='hide', caption="An open and reproducible research workflow."}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

@@

When making your science more open and reproducible, methods, software used (including things like R packages), etc. should be cited properly. This allows end users to identify what was used and identify the methods used more accurately. Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research. This also helps ensure that you as a researcher are able to reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, _e.g._ a package version, what effect it had on your research.

@@

- provide full description for equipments, etc.

- rOpenSci Reproducible Research: http://ropensci.github.io/reproducibility-guide/sections/introduction/

@@

### Source Code
